An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2010-12-14 paper.tex
Added acceptRate plots, Makefile, and Matlab script for plot.

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{color}

@@

From the set of points output by a single-model MCMC,
$\{\vtheta_i^{(j)} | j = 1, 2, \ldots \}$, all lying in the $M_i$
parameter space, we would like to construct a set of ``neighborhoods''
associated with each of the sample points.  The neighborhoods should
be non-overlapping and fill parameter space.

\ilya{Mention example of bricks from \cite{Littenberg2009}.}

@@

>>>>

\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{color}
\usepackage{graphicx}

@@

From the set of points output by a single-model MCMC,
$\{\vtheta_i^{(j)} | j = 1, 2, \ldots \}$, all lying in the $M_i$
parameter space, we would like to construct a set of ``neighborhoods''
associated with each of the sample points.  The neighborhoods should
be non-overlapping and fill parameter space.  To draw a proposed jump
from an approximation to the model PDF, we select a point uniformly
from the $\vtheta^{(j)}_i$, find its associated neighborhood, and then
draw the proposed jump uniformly from the neighborhood.  Since the
MCMC points are distributed according to the posterior PDF for $M_i$,
this procedure produces proposed jumps that are approximately
distributed according to the posterior PDF.  In fact, the proposed
jumps are drawn from a piecewise-constant (i.e.\ constant on each
neighborhood) interpolation of the PDF.

There are various techniques that could be used to construct the set
of neighborhoods associated with each point.
Ref.~\cite{Littenberg2009} decomposed parameter space into
constant-volume ``bricks'' whose size was set by the typical size of
the peaks of the PDF.  Each point was associated with the brick that
contained it.  Unfortunately, this process does not guarantee that
every brick contains at least one point, which is required for the
jump proposal to cover the entire model parameter space.  The solution
to this problem was to add a uniform distribution to the proposal PDF,
in the form of one ``fictitious'' point per brick.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.8\textwidth]{acceptRate}
  \end{center}
  \caption{\label{fig:acceptRate} The inter-model acceptance rate as a
    function of boxing number for the RJMCMC described in the text.}
\end{figure}
